Spfy: an integrated graph database for real-time prediction of bacterial phenotypes and downstream comparative analyses

### 2018-06-15 paper-webserver.tex

\author[1]{Kevin K Le\thanks{kevin.le@canada.ca}}
\author[1]{Matthew D Whiteside}
\author[1]{James E Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing\thanks{chad.laing@canada.ca}}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

Spfy primarily uses Blazegraph \url{https://github.com/blazegraph/database} for storage along with MongoDB to cache a hash table for duplicate checking.
The cache allows Spfy to more efficiently check for duplicate files in Blazegraph than would be possible through a search of the graph structure.
MongoDB is also used to support the

@@

However, unlike these workflow managers, Spfy is designed to help solve the re-computation of analyses by storing results in a graph database for downstream comparative studies \ref{db_comparison}. This allows Spfy to, for example, perform population-wide analyses on varied data from multiple diverse individual software.

@@

\section{ACKNOWLEDGEMENTS}

@@

\section{APPENDIX}

\section{SUPPLEMENTARY INFORMATION}

% Again, label panes as a) and b), then reference in the caption
\begin{figure}[!htb]
\minipage{0.5\textwidth}
  \includegraphics[width=\linewidth]{images/spfy_indivs.png}
\endminipage\hfill
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches.png}
\endminipage
\caption{Runtimes of Spfy's analysis modules. A: 100 genomes were run individually, with each coloured dot representing the runtime of a separate analysis module. The blue line indicates the average actual runtime per file after accounting for parallelization. B: Average runtime when multiple genomes are enqueued together. As indicated by the line, the average runtime per genome in consistent when running more than one file.}\label{fig:supp_spfy_performance}
\end{figure}

>>>>

\author[1]{Kevin K Le\thanks{kle009@uottawa.ca}}
\author[1]{Matthew D Whiteside}
\author[1]{James E Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing\thanks{chad.laing@canada.ca}}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

Spfy primarily uses Blazegraph \url{https://github.com/blazegraph/database} for storage along with MongoDB to cache a hash table for duplicate checking.
The cache allows Spfy to more efficiently check for duplicate files in Blazegraph than would be possible through a search of the graph structure.
MongoDB is also used to support the synchronized user sessions feature of the website.

@@

However, unlike these workflow managers, Spfy is designed to help solve the re-computation of analyses by storing results in a graph database for downstream comparative studies (Table \ref{db_comparison}). This allows Spfy to, for example, perform population-wide analyses on varied data from multiple diverse individual software.

@@

@@
